---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%", 
  fig.width = 10, 
  fig.height = 5,
  dpi = 300
)
```

# ggkeyboard

ggkeyboard lets you plot a keyboard and change the colours on it. It's cute.

You can install ggkeyboard from github:

``` r 
# install.packages("devtools")
devtools::install_github("sharlagelfand/ggkeyboard", ref = "main")
```

Plot a keyboard using `ggkeyboard()`. The default is very cute:

```{r}
library(ggkeyboard)

ggkeyboard()
```

You can change the colours, font, sizes, etc. This keyboard is inspired by the [Drop + Zambumon MT3 Serika Custom Keycap Set](https://drop.com/buy/drop-zambumon-mt3-serika-custom-keycap-set):

```{r}
ggkeyboard(
  keyboard_colour = "#51504A", modifier_colour = "#ffce00", accent_colour = "#454A49",
  alphanum_colour = "#EDEDD8", arrow_colour = "#454A49", font_family = "Courier",
  background_colour = "lightgrey", light_colour = "#8aff2b"
)
```

This one is inspired by the [Melgeek MG Wahtsy ABS Doubleshot Keycap Set](https://drop.com/buy/melgeek-mg-wahtsy-abs-doubleshot-keycap-set):

```{r}
ggkeyboard(
  keyboard_colour = "#E5E7EB", modifier_colour = "#155E90", accent_colour = "#F9B668",
  alphanum_colour = "#DFDED9", arrow_colour = "#155E90", background_colour = "#F0F0F0",
  text_colour = "#f97600"
)
```

and this one by the [Domikey ABS Doubleshot SA Cyberpunk Pumper Keycap Set](https://drop.com/buy/domikey-abs-doubleshot-sa-cyberpunk-pumper-keycap-set):

```{r}
ggkeyboard(
  keyboard_colour = "#313131", modifier_colour = "#FF4893", accent_colour = "#00A8E8",
  alphanum_colour = "#6F4CA4", arrow_colour = "#00A8E8", background_colour = "#F0F0F0",
  text_colour = "white"
)
```

`ggkeyboard()` defaults to using a tenkeyless keyboard, available in `tkl`:

```{r}
head(tkl)
```

You can use an ISO keyboard and layout by changing the `data` and `layout`:

```{r}
ggkeyboard(tkl_iso, layout = "iso")
```

