---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%", 
  fig.width = 10, 
  fig.height = 4.5,
  dpi = 300
)
```

# ggkeyboard

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

ggkeyboard lets you plot a keyboard and change the colours on it. This package is very experimental, so expect breaking changes as I work through making all the customization options as friendly as possible.

You can install ggkeyboard from github:

``` r 
# install.packages("devtools")
devtools::install_github("sharlagelfand/ggkeyboard", ref = "main")
```

Plot a keyboard using `ggkeyboard()`. The default is very cute:

```{r pastel}
library(ggkeyboard)

ggkeyboard()
```

You can change the colours, font, sizes, etc. There are a few built in colour palettes, available via `keyboard_palette()`:

```{r palette}
library(scales)

show_col(keyboard_palette("serika"))
```

This keyboard is inspired by the [Drop + Zambumon MT3 Serika Custom Keycap Set](https://drop.com/buy/drop-zambumon-mt3-serika-custom-keycap-set):

```{r serika}
ggkeyboard(palette = keyboard_palette("serika"))
```

This one is inspired by the [Melgeek MG Wahtsy ABS Doubleshot Keycap Set](https://drop.com/buy/melgeek-mg-wahtsy-abs-doubleshot-keycap-set):

```{r wahtsy}
ggkeyboard(palette = keyboard_palette("wahtsy"))
```

and this one by the [Domikey ABS Doubleshot SA Cyberpunk Pumper Keycap Set](https://drop.com/buy/domikey-abs-doubleshot-sa-cyberpunk-pumper-keycap-set):

```{r cyberpunk}
ggkeyboard(palette = keyboard_palette("cyberpunk"))
```

`ggkeyboard()` defaults to using a tenkeyless keyboard, available in `tkl`:

```{r tkl}
head(tkl)
```

There is also a full keyboard layout available via `full`. This palette is based off the [Varmilo VA108 Fullsize Keyboard](https://drop.com/buy/varmilo-108-keyboard)

```{r full}
ggkeyboard(full, palette = keyboard_palette("varmilo"), font_size = 2.75)
```

a 60% layout available via `sixty_percent`:

```{r sixty}
ggkeyboard(sixty_percent)
```

and a mac layout, based off the Apple magic keyboard:

```{r mac}
ggkeyboard(mac, font_family = "Arial Unicode MS", palette = keyboard_palette("magic"))
```

You can use an ISO layout by changing `layout` to "iso", for any of the given keyboards:

```{r iso}
ggkeyboard(tkl, layout = "iso")
```

