---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%", 
  fig.width = 10, 
  fig.height = 5,
  dpi = 300
)
```

# ggkeyboard

ggkeyboard lets you plot a keyboard and change the colours on it. It's cute.

You can install ggkeyboard from github:

``` r 
# install.packages("devtools")
devtools::install_github("sharlagelfand/ggkeyboard", ref = "main")
```

Plot a keyboard using `ggkeyboard()`. The default is very cute:

```{r}
library(ggkeyboard)

ggkeyboard()
```

You can change the colours, font, sizes, etc. There are a few built in colour palettes, available via `keyboard_palette()`:

```{r}
library(scales)

show_col(keyboard_palette("serika"))
```

This keyboard is inspired by the [Drop + Zambumon MT3 Serika Custom Keycap Set](https://drop.com/buy/drop-zambumon-mt3-serika-custom-keycap-set):

```{r}
ggkeyboard(palette = keyboard_palette("serika"))
```

This one is inspired by the [Melgeek MG Wahtsy ABS Doubleshot Keycap Set](https://drop.com/buy/melgeek-mg-wahtsy-abs-doubleshot-keycap-set):

```{r}
ggkeyboard(palette = keyboard_palette("wahtsy"))
```

and this one by the [Domikey ABS Doubleshot SA Cyberpunk Pumper Keycap Set](https://drop.com/buy/domikey-abs-doubleshot-sa-cyberpunk-pumper-keycap-set):

```{r}
ggkeyboard(palette = keyboard_palette("cyberpunk"))
```

`ggkeyboard()` defaults to using a tenkeyless keyboard, available in `tkl`:

```{r}
head(tkl)
```

You can use an ISO keyboard and layout by changing the `data` and `layout`:

```{r}
ggkeyboard(tkl_iso, layout = "iso")
```

